---
title: "Filter Data"
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(shiny)
library(dplyr)
# Random Data Frame
df <- data.frame(Country = paste("Country", 1:100, sep = "_"), 
                 Revenue = rnorm(n = 100, mean = 5000, sd = 2000))
```

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
ui <- fluidPage(
  
  # App title ----
  titlePanel("Downloading Data"),
  
  # Sidebar layout with input and output definitions ----
  sidebarLayout(
    
    # Sidebar panel for inputs ----
    sidebarPanel(
      
      # Input: Choose dataset ----
      selectInput("dataset", "Choose a Country",
                  choices = as.character(unique(df$Country))),
      
      # Button
      downloadButton("downloadData", "Download")
      
    ),
    
    # Main panel for displaying outputs ----
    mainPanel(
      
      tableOutput("table")
      
    )
    
  )
)

# Define server logic to display and download selected file ----
server <- function(input, output) {
  
  # Reactive value for selected dataset ----
  datasetInput <- reactive({
      df %>% filter(Country ==input$dataset)
  })
  
  # Table of selected dataset ----
  output$table <- renderTable({
    datasetInput()
  })
  
  # Downloadable csv of selected dataset ----
  output$downloadData <- downloadHandler(
    filename = function() {
      paste(as.character(input$dataset), ".csv", sep = "")
    },
    content = function(file) {
      write.csv(datasetInput(), file, row.names = FALSE)
    }
  )
  
}
# Create Shiny app ----
shinyApp(ui, server)
```