

Taken together these five reviews collected a total of `r nrow(dt.Scales[dt.Scales$Review != "own",])` scales, of which `r nrow(dt.Scales[dt.Scales$Duplicate == "Duplicate" & dt.Scales$Review != "own",])` were duplicates. From our own review we added `r nrow(dt.Scales[dt.Scales$Review == "own review",])` additional validation studies. After removing duplicates this meant that we considered a total of `r nrow(dt.Scales[dt.Scales$Duplicate == "Unique",])` unique scales for our coding. Of these scales we ultimately had to exclude `r nrow(dt.Scales[!is.na(dt.Scales$Comment),])`, because they were either not accessible or did not fit the the topic of our review (see Table \@ref(tab:ScalesExclusion)). The remaining `r nrow(dt.Scales[dt.Scales$Duplicate == "Unique" & is.na(dt.Scales$Comment),])` scales are listed in Table \@ref(tab:ScaleTbl).  

```{r ScalesExclusion, results='asis'}
# data.frame(table(Exclusion = dt.Scales$Comment)) %>%
#   arrange(desc(Freq)) %>%
#   kbl(., caption = "Reasons for Exclusion",
#       format = "html",
#       col.names = c("Exclusion Reason",
#                     "Frequency")) %>%
#   kable_classic(full_width = F, 
#                 lightable_options = "hover", 
#                 html_font = "Cambria")

data.frame(table(Exclusion = dt.Scales$Comment)) %>%
  arrange(desc(Freq)) %>%
  kbl(., 
      label = "ScalesExclusion",
      caption = "Reasons for Exclusion",
      format = "latex",
      col.names = c("Exclusion Reason",
                    "Frequency"), 
      linesep = "",
      booktabs = T,
      align = c("l", "c"))  %>%
  kable_styling(latex_options = c("repeat_header"),
                position = "left") %>%
  save_kable("Tables/ScalesExclusion.tex")
```

```{r ScaleTbl}
# dt.Scales.Included %>%
#   mutate(SourceShort = stri_replace_all_fixed(Source,
#                                          pattern = c("@Celenk2011", "@Maestas2000", "@Matsudaira2006", "@Wallace2010", "@Zane2004", "own review"), 
#                                          replacement = c("CEL", "MAE", "MAT", "WAL", "ZAN", "OWN"), 
#                                          vectorize_all = FALSE)) %>%
#   dplyr::select(Scale, Reference, `Source ^a^` = SourceShort, 
#                 Affect, 	Behavior,	Cognition,	Desire,
#                 `domain scale`,Sample,	`Includes Majority`, 
#                 `Host Country Comb`,	`Origin Country Comb`) %>%
#   mutate_at(vars(Affect, 	Behavior,	Cognition, Desire), ~replace_na(., 0)) %>%
#   kbl(., caption = "Integration Scales",
#       format = "html") %>%
#   add_footnote(c("CEL = @Celenk2011, MAE = @Maestas2000, MAT = @Matsudaira2006, WAL = @Wallace2010, ZAN = @Zane2004, OWN = own review (only additional)"), 
#                notation = "alphabet") %>%
#   kable_classic(full_width = F, 
#                 lightable_options = "hover", 
#                 html_font = "Cambria") %>%
#    scroll_box(width = "110%", height = "750px")

dt.Scales.Included %>%
  mutate(SourceShort = stri_replace_all_fixed(Source,
                                         pattern = c("@Celenk2011", "@Maestas2000", "@Matsudaira2006", "@Wallace2010", "@Zane2004", "own review"), 
                                         replacement = c("CEL", "MAE", "MAT", "WAL", "ZAN", "OWN"), 
                                         vectorize_all = FALSE)) %>%
  dplyr::select(Scale, Reference, `Source [note]"` = SourceShort, 
                Affect, 	Behavior,	Cognition,	Desire,
                `domain scale`,Sample,	`Includes Majority`, 
                `Host Country Comb`,	`Origin Country Comb`) %>%
  mutate_at(vars(Affect, 	Behavior,	Cognition, Desire), ~replace_na(., 0)) %>%
  kbl(., 
      label = "ScaleTbl",
      caption = "Cultural Adaptation Scales",
      format = "latex",
      linesep = "",
      booktabs = T,
      longtable = T,
      align = c("l", "c"))  %>%
  add_footnote(c("CEL = @Celenk2011, MAE = @Maestas2000, MAT = @Matsudaira2006, WAL = @Wallace2010, ZAN = @Zane2004, OWN = own review (only additional)"), 
               notation = "alphabet") %>%
  kable_styling(latex_options = c("repeat_header"),
                position = "left") %>%
  save_kable("Tables/ScaleTbl.tex")
```
